---
title: "A simple look into tidygapminder"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidygapminder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package aims to make really easy to tidy data retrieved from [Gapminder](https://www.gapminder.org). A the begining is:

```{r}
library(tidygapminder)
```

When you have loaded the package you are now in possesion of two super powers (functions): tidy_indice and tidy_bunch.

## tidy_indice

`tidy_indice` fucntion tidy as explain above tidy a data sheet downloaded on Gapminder. This data sheet can be either in csv or xlsx as indicated on the gapminder site.

`tidy_indice` take as argument the path to the file and return the data as a tidy data frame.

```{r}
filepath <- system.file("extdata", "life_expectancy_years.csv", package = "tidygapminder")

tidy_indice(filepath)
```


## tidy_bunch

`tidy_bunch` makes use of `tidy_indice` to tidy a whole set of data sheets and have the options to merge all data frames into one big data frame with `merge` set to `TRUE`:

```{r}
dir_path <- system.file("extdata", "gapminder", package = "tidygapminder")

tidy_bunch(dir_path, merge = TRUE)
```

Enjoy!!!
